Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures

### 2017-09-26 regularity.tex
typos

Let us now consider the situation where $n < i \leq 2n-1$. We start with the special case where $i = 2n-1$. Then, we have only one term in the sum
\begin{align*}
\sum_{j+l = i}(j+1)a_{j+1}a_l  (r^{j+1}- r^l) &= \sum_{l=n}^{n}(2n-1-l+1)a_{2n-1-l+1}a_l  (r^{2n-1-l+1}- r^l) \\
&= na_{n}a_n  (r^{n}- r^n) \\
& = 0.
\end{align*}Now, let $n < i < 2n-1$, we follow a similar procedure as before to manipulate the sum
\begin{align*}
\sum_{j+l = i}(j+1)a_{j+1}a_l  (r^{j+1}- r^l) &= \sum_{l=i-n + 1}^{n}(i-l+1)a_{i-l+1}a_l  (r^{i-l+1}- r^l) \\
& = \sum_{l=i-n + 1}^{n}(i-l+1)c_l \\
& = \sum_{k=1}^{2n-i}(n-k+1)c_{i-n+k} \\
& = \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1)c_{i-n+k}\\
&+  (n-(2n-i-k+1)+1)c_{i-n+(2n-i-k+1)} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1)c_{i-n+k} +  (i-n+k)c_{n-k+1} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1)c_{i-n+k} -  (i-n+k)c_{i-n+k} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1-(i-n+k))c_{i-n+k} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(2n-i-2k+1))c_{i-n+k}.
\end{align*}It is now easy to verify that $(2n-i-2k+1)$ and $c_{i-n+k}$ are positive if $k \leq n - (i+2)/2$ which holds since $k$ ranges from $1$ to $\lfloor n - i/2 \rfloor$. The floor function is again used when we sum over pairs of terms since if $i$ is odd there is zero-term. 
Since all the coefficients are non-negative and the $k \geq 2$, the derivative is positive. This implies that the original function is increasing.

%$$
%C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}|s(l + 1,j)| \ (rk)^j \Ri.
%$$ Derivatives are obtained easily from this form
%$$&=  \sum_{k=i-n + 1}^{\lfloor n - i/2 \rfloor}(i-l+1)c_k + (i-(n-k + 1)+1)c_{n-k+1} 
%\frac{d}{dk}C(n,k) = \sum_{l=0}^{n-1} b_l \Le\sum_{j=1}^{l+1}j \ |s(l + 1,j)| \ k^{j-1}\Ri
%$$and
%$$
%\frac{d}{dk}C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}j \ r^{j} \ |s(l + 1,j)| \ k^{j-1}\Ri.
%$$
\end{document}

>>>>

Let us now consider the situation where $n < i \leq 2n-1$. We start with the special case where $i = 2n-1$. Then, we have only one term in the sum
\begin{align*}
\sum_{j+l = i}(j+1)a_{j+1}a_l  (r^{j+1}- r^l) &= \sum_{l=n}^{n}(2n-1-l+1)a_{2n-1-l+1}a_l  (r^{2n-1-l+1}- r^l) \\
&= na_{n}a_n  (r^{n}- r^n) \\
& = 0.
\end{align*}Now, let $n < i < 2n-1$, we follow a similar procedure as before to manipulate the sum
\begin{align*}
\sum_{j+l = i}(j+1)a_{j+1}a_l  (r^{j+1}- r^l) &= \sum_{l=i-n + 1}^{n}(i-l+1)a_{i-l+1}a_l  (r^{i-l+1}- r^l) \\
& = \sum_{l=i-n + 1}^{n}(i-l+1)c_l \\
& = \sum_{k=1}^{2n-i}(n-k+1)c_{i-n+k} \\
& = \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1)c_{i-n+k}\\
&+  (n-(2n-i-k+1)+1)c_{i-n+(2n-i-k+1)} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1)c_{i-n+k} +  (i-n+k)c_{n-k+1} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1)c_{i-n+k} -  (i-n+k)c_{i-n+k} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(n-k+1-(i-n+k))c_{i-n+k} \\
&= \sum_{k=1}^{\lfloor n - i/2 \rfloor}(2n-i-2k+1)c_{i-n+k}.
\end{align*}It is now easy to verify that $(2n-i-2k+1)$ and $c_{i-n+k}$ are positive if $k \leq n - (i-1)/2$ which holds since $k$ ranges from $1$ to $\lfloor n - i/2 \rfloor$. The floor function is again used when we sum over pairs of terms since if $i$ is odd there is zero-term. 
Since all the coefficients are non-negative and the $k \geq 2$, the derivative is positive. This implies that the original function is increasing.

%$$
%C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}|s(l + 1,j)| \ (rk)^j \Ri.
%$$ Derivatives are obtained easily from this form
%$$&=  \sum_{k=i-n + 1}^{\lfloor n - i/2 \rfloor}(i-l+1)c_k + (i-(n-k + 1)+1)c_{n-k+1} 
%\frac{d}{dk}C(n,k) = \sum_{l=0}^{n-1} b_l \Le\sum_{j=1}^{l+1}j \ |s(l + 1,j)| \ k^{j-1}\Ri
%$$and
%$$
%\frac{d}{dk}C(n,rk) = \sum_{l=0}^{n-1} b_l \Le \sum_{j=1}^{l+1}j \ r^{j} \ |s(l + 1,j)| \ k^{j-1}\Ri.
%$$
\section{Terms $a_j$ sum to one}
\begin{align*}
\sum_{j=1}^{n}a_j &=\sum_{j=1}^{n} \Le \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \ |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \Le \sum_{j=1}^{n} |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \Le \sum_{j=0}^{l-1} |s(l + 1,j)| \Ri \\
&= \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}l!} \ (l+1)! \\
& =  \sum_{l=0}^{n-1} \frac{(n-1)^{\underline{l}}}{n^{l+1}}(l+1)
\end{align*}
\end{document}
